A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
SIPping
title case
Cites

\section{The \McSplit\ algorithm}

@@

Experiments were performed on machines with dual Intel Xeon E5-2640 v2 CPUs and
64GBytes RAM. Our algorithm was implemented in C++ and compiled using g++
5.3.0. For comparison, we used the implementations of ?? cite clique, kdown,
CP.

@@

?? kdown only does undirected unlabelled unconnected

?? There are five contours:
the clique encoding \citep{DBLP:conf/cp/McCreeshNPS16}, CP-FC
\citep{DBLP:conf/cp/NdiayeS11}, \McSplit\, AND TWO OTHERS.  WE NEED CITATIONS
FOR THESE AND ALSO NEED TO CLEAN UP THE LABELS ON THE GRAPHS.

@@

\paragraph{Large subgraph isomorphism instances} We also ran the algorithms on
a set of 5725 larger instances used in recent studies of subgraph
isomorphism~\cite{thelionpaper} and maximum common
subgraph~\cite{UpcomingAAAIPaper}.  This benchmark set includes real-world
graphs and graphs generated using random models.  Pattern graphs range from 4
vertices to 900 with a median of 80; target graphs range from 10 vertices to
6671 with a median of 561.  Cumulative runtimes including the kdown algorithm
from~\cite{UpcomingAAAIPaper} which was the previous state of the art for this
benchmark, are in \cref{figure:sip-cumulative}.  This is a challenging set of
instances, and more than half of the instances cannot be solved within a
timeout of 1000 seconds by any of the solvers. Moreover the CP-FC algorithm and
the clique encoding run out of memory on many of the instances.  \McSplit\
is the strongest solver overall for this dataset.

\begin{figure}[t]
    \centering
    \includegraphics*{gen-graph-sip-cumulative.pdf}
    \caption{Cumulative run times, SIP instances}\label{figure:sip-cumulative}
\end{figure}

>>>>

\section{The \McSplit\ Algorithm}

@@

Experiments were performed on machines with dual Intel Xeon E5-2640 v2 CPUs and
64GBytes RAM. Our algorithm was implemented in C++ and compiled using g++
5.3.0. For comparison, we compare against the best constraint programming
implementations of \citet{DBLP:conf/cp/NdiayeS11} and
\citet{DBLP:conf/cp/McCreeshNPS16} (CP-FC in the unlabelled cases, and CP-MAC
in the labelled cases, using both branching and filtering for connected
subgraphs), the clique encodings of \citet{DBLP:conf/cp/McCreeshNPS16}, and the
$k\downarrow$ algorithm of \citet{UpcomingAAAIPaper} (which only supports
unlabelled, undirected, unconnected instances).

@@

@@

\paragraph{Large subgraph isomorphism instances} We also ran the algorithms on
a set of 5725 larger instances used in recent studies of subgraph
isomorphism~\citep{DBLP:conf/lion/KotthoffMS16} and maximum common
subgraph~\citep{UpcomingAAAIPaper}.  This benchmark set includes real-world
graphs and graphs generated using random models.  Pattern graphs range from 4
vertices to 900 with a median of 80; target graphs range from 10 vertices to
6671 with a median of 561.  Cumulative runtimes including the kdown algorithm
from~\citep{UpcomingAAAIPaper} which was the previous state of the art for this
benchmark, are in \cref{figure:sip-cumulative}.  This is a challenging set of
instances, and more than half of the instances cannot be solved within a
timeout of 1000 seconds by any of the solvers. Moreover the CP-FC algorithm and
the clique encoding run out of memory on many of the instances.  \McSplit\
is the strongest solver overall for this dataset.

\begin{figure}[t]
    \centering
    \includegraphics*{gen-graph-sip-cumulative.pdf}
    \caption{Cumulative numbers of instances solved over time for the maximum
    common connected subgraph problem on the large subgraph isomorphism benchmark
    suite.} \label{figure:sip-cumulative}
\end{figure}
